---
title             : "d2m Manuscript"
shorttitle        : "d2m"

author: 
  - name          : "Songyang Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "60637"
    email         : "songyangzhang@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Janet Geipel"
    affiliation   : "2"
    role:
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "University of Exeter"

authornote: |
  Department of Psychology, University of Chicago 
  Department of Marketing, University of Exeter 


abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r}
#Assignment 5
source("d2m_intro.R")
greeting_output <- hello_world("Dr. Dowling", TRUE)
print(greeting_output)
```
The following is the continuation of the assignment 5 
#Introduction 
## HPV Information 
### Safety of HPV vaccination 

Unordered list
- HPV vaccination 
- COVID-19 vaccination 
- Influenza vaccination 

ordered list
1. First shot 
2. Second shot 
3. Third shot 

**the importance of vaccination**
*HPV vaccination only for people who are lower than 26 years old*

[CDC Website](https://www.cdc.gov/std/hpv/default.htm)

<!-- read website carefully HTML -->



```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
