---
title             : "d2m Manuscript"
shorttitle        : "d2m"

author: 
  - name          : "Songyang Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "60637"
    email         : "songyangzhang@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Janet Geipel"
    affiliation   : "2"
    role:
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "University of Exeter"

authornote: |
  Department of Psychology, University of Chicago 
  Department of Marketing, University of Exeter 


abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r}
#Assignment 5
source("d2m_intro.R")
greeting_output <- hello_world("Dr. Dowling", TRUE)
print(greeting_output)
```
The following is the continuation of the assignment 5 
#Introduction 
## HPV Information 
### Safety of HPV vaccination 

Unordered list
- HPV vaccination 
- COVID-19 vaccination 
- Influenza vaccination 

ordered list
1. First shot 
2. Second shot 
3. Third shot 

**the importance of vaccination**
*HPV vaccination only for people who are lower than 26 years old*

[CDC Website](https://www.cdc.gov/std/hpv/default.htm)

<!-- read website carefully HTML -->

```{r}
#Assignment 6 
#read data and data cleaning
raw <- read.csv("HPVMaleVaccine_Data_Study1.csv")
data <- subset(raw, Finished==1 & Duration..in.seconds. > 0 &
                 attention_check_1==5 & honest_check==1 & age < 27)
raw_finished <-subset(raw, Finished==1 & Duration..in.seconds. > 0 & 
                        consent_agree ==1 & income > 0)
raw_finished$Exclusion <- ifelse(raw_finished$Finished!=1|raw_finished$Duration..in.seconds.==0|
                                   raw_finished$attention_check_1!=5|raw_finished$honest_check!=1|
                                   raw_finished$age>=27,1,0)

```

```{r}
#Assignment 6 continued 
#for the intermediate dataset, we only select people who are greater than 20 years old in 2023, and then add 1 to all the participant's age because it is 2024. 
library(dplyr)
intermediate_data <- data %>%
  select(age) %>%
  filter(age > 20) %>% 
  mutate(age_new = age + 1)
write.csv(intermediate_data, "intermediate_data.csv")

```

## Assginment 9 
The data prep is completed in the first part of assignment 6. According to my previous document, the preparation of the data primarily focus on excluding the participant who does not satisfy the preliminary pre-screening criteria and the participants fail to pass the attention check. 
For further analysis of the dataset, I will use "data" as the cleaned data for analysis. The intermediate dataset is for assignment purposes ad will not be used in further analysis. 

<!--
Assignment 10 
imagine the image that I want to do: 
the first plot is a bar graph representing the HPV vaccination intention for different treatment conditions, I want the graph also have SE for each condition of the HPV vaccination intention. 
For the second graph, I also want the bar graph representing the interaction plot, showing moderation relationship between two conditions, by one possible moderator. I also want SE of vaccination intention shown on the graph. 
In conclusion, the two graph are all bar graph, with condition on x-axis, and HPV vaccination intention on y-axis. For the second graph, the added element would be one possible moderator, showing in the graph using different colors. 
-->

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

##Assignment 11
I want to add an explanation before assignment 11. I have talked to Dr. Dowling last week about switching dataset as I have a new pilot data on the use of identity-based vs. person-based language on stigmatization attitude and prosocial behavior intention. As a result

```{r}
#Assignment 11 
#load data 
data1 <- read.csv("Pilot_homelessness.csv")
#delete the first 12 rows, which is used for preview purposes
data1 <- data1[-(1:12), ] 
#drop duplicated prolific id 
data1 <- data1 %>% distinct(ProlificID, .keep_all = TRUE)

#boxplot by condition, use the minimal theme to clean-up the graph
plot1 <- ggplot(data=data1, aes(x=Condition, y=as.numeric(beha1_donation_1))) + 
  geom_boxplot() +
  theme_minimal() +  
  labs(x = "Condition", y = "Amount of Donation") + 
  NULL
plot1 
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
